---
title: "Appendix"
output: pdf_document
date: "2022-12-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Appendix A: Data Cleaning
```{r, message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(skimr)
library(dplyr)
library(gt)
library(scales)
library(broom)
```

### Disney movies total gross
```{r, message=FALSE, warning=FALSE}
disney <- read_csv("/Users/christinalopez/Desktop/STAT471_F22/datasets/disney/disney_movies_total_gross.csv")
skim_without_charts(disney)
```

Clean up variables and drop NA's.

```{r}
disney2 <- disney |>
  mutate(genre = factor(genre), 
         rating = factor(MPAA_rating, levels = c("G", "PG", "PG-13", "R")), 
         gross = parse_number(inflation_adjusted_gross),
         release_date = as.Date(release_date, format = "%b %d, %Y"),
         release_year = as.numeric(format(release_date, "%Y")),
         gross_million = round(gross/1000000, digits = 1),
         gross_K = round(gross/1000, digits =3)) |>
  select(-total_gross, -inflation_adjusted_gross, -MPAA_rating ) |>
  drop_na() |>
  filter(release_year >= 1992)
head(disney2)
```

### Disney revenue 1991 - 2016

```{r, message=FALSE, warning=FALSE}
revenue <- read_csv("/Users/christinalopez/Desktop/STAT471_F22/datasets/disney/disney_revenue_1991-2016.csv")
skim_without_charts(revenue)
```

### movies.revenue

```{r}
movies.revenue <- disney2 |>
  mutate(Year = release_year) |> 
  inner_join(revenue, by = c("Year" = "Year")) 
head(movies.revenue)
```

### yearly.summary

```{r}
yearly.summary <- movies.revenue |>
  group_by(Year, Total) |>
  summarize(movie_count = n()) |>
  rename(total_revenue = Total) |>
  ungroup()
head(yearly.summary)
```


### movies.revenue2

```{r}
movies.revenue2 <- movies.revenue |>
  mutate(action = ifelse(genre == "Action", 1, 0),
         adventure = ifelse(genre == "Adventure",1,0),
         musical = ifelse(genre == "Musical", 1, 0),
         drama = ifelse(genre == "Drama", 1, 0),
         comedy = ifelse(genre == "Comedy", 1, 0)) |>
  filter(Year >= 1992)
head(movies.revenue2)
```

### yearly.summary2

```{r}
yearly.summary2 <- movies.revenue2 |>
  group_by(Year, Total) |>
  summarize(movie_count = n(),
            action_count = sum(action),
            adventure = sum(adventure),
            musical = sum(musical),
            drama = sum(drama),
            comedy = sum(comedy)) |>
  rename(total_revenue = Total) |>
  ungroup()

head(yearly.summary2)
```


# Appendix B: Exporatory Data Analysis

### Disney movies total gross

```{r}
skim_without_charts(disney2)
```

```{r}
colors = c("thistle3", "thistle4", "rosybrown3", "rosybrown4")
disney2 |>
  group_by(rating) |>
  summarize(n = n()) |>
  ggplot(aes(x = reorder(rating, -n), y = n)) + 
  geom_col(aes(fill = reorder(rating,n)), color = "black", size = 0.2) +   
  scale_fill_manual(values = colors) +
  ggtitle("Top Movie Ratings")+ labs(x = "MPAA Rating", y = "Count") + 
  theme_minimal() + theme(legend.position = "none")
```


```{r}
disney2 |>
  select(release_year) |>
  filter(release_year >= 1991) |>
  group_by(release_year) |>
  summarise(n = n()) |>
  ggplot(aes(x = release_year, y = n)) + 
  geom_col(fill = "thistle3", color = "black", size = 0.2)+ 
  ggtitle("Histogram of Movie Release Year") + 
  theme_minimal() + labs(x = "Release Year", y = "Count")
```


### Yearly summary 

```{r}
yearly.summary |>
  ggplot(aes(x = total_revenue)) +
  geom_histogram(bins = 15, fill = "thistle3", color = "black", size = 0.2)+ 
  ggtitle("Histogram of Yearly Revenue For Disney (Millions of  US $)") + 
  theme_minimal() + labs(x = "Yearly Revenue ($ M)", y = "Count")
```

# Appendix C: What are the highest and lowest grossing movies?

### Highest

```{r}
movies.revenue2 |>
  select(movie_title,genre,rating,Year,gross_million) %>%
  arrange(desc(gross_million)) %>%
  head(8) %>%
  gt(rowname_col = "movie_title") %>%
  tab_header(
    title = md("Summary of the **$ Gross Revenue Per Movie** from 1992 to 2016"),
    subtitle = md("Million US $")) %>%
  tab_source_note(
    source_note = md("This file contains data on the Revenue and Gross of the Walt Disney Company from 1992 to 2016")) %>%
  tab_caption(
    caption = md("Source: Disney Character Success from Kaggle")) %>%
  tab_stubhead(label = md("Movies")) %>%
  opt_table_font(font = google_font("Mouse Memoirs"), weight = 100) %>%
  cols_label(genre = "Genre",
             rating = "Rating",
             gross_million = "$ Gross") %>%
  data_color(
    columns = gross_million,
    fn = scales::col_numeric(
      palette = "RdPu",
      domain = c(1000, 480))) 
```

### Lowest 

```{r}
movies.revenue2 |>
  select(movie_title,genre,rating,Year,gross_million) %>%
  arrange(gross_million) %>%
  head(8) %>%
  gt(rowname_col = "movie_title") %>%
  tab_header(
    title = md("Summary of the **Gross Revenue Per Movie** from 1992 to 2016"),
    subtitle = md("Million US $")) %>%
  tab_source_note(
    source_note = md("This file contains data on the Revenue and Gross of the Walt Disney Company from 1992 to 2016")) %>%
  tab_caption(
    caption = md("Source: Disney Character Success from Kaggle")) %>%
  tab_stubhead(label = md("Movies")) %>%
  opt_table_font(font = google_font("Mouse Memoirs"), weight = 100) %>%
  cols_label(genre = "Genre",
             rating = "Rating",
             gross_million = "$ Gross") %>%
  data_color(
    columns = gross_million,
    fn = scales::col_numeric(
      palette = "magma",
      domain = c(0, 0.8))) 
```

# Appendix D: What is the most common genre produced by Disney?

```{r}
colors4 = c("thistle4", "thistle3", "rosybrown4", "rosybrown3", "lightpink4", "lightpink3")
disney2 |>
  select(genre) |>
  group_by(genre) |>
  summarise(n = n()) |>
  head(6) |>
  ggplot(aes(x = reorder(genre, -n), y = n)) + 
  geom_col(aes(fill = reorder(genre, -n)), color = "black", size = .2) +
  scale_fill_manual(values = colors4) +
  ggtitle("Top genres") + labs(x = "Genre", y = "Count") + 
  theme_minimal() + theme(legend.position = "none")
```

# Appendix E: Which variables best predict the actual revenue per year?

### AIC 

```{r}
n = nrow(yearly.summary2)
mod0 = lm(total_revenue ~ 1, data = yearly.summary2)
mod.all = lm(total_revenue ~., data = yearly.summary2)
step(mod0, scope = list(lower = mod0, upper = mod.all))
```

### AIC Model

```{r}
mod.full <- yearly.summary2 |>
  lm(formula = total_revenue ~ comedy + movie_count)
summary(mod.full)
```

### Model assumptions

```{r}
yearly.summary2 |>
  ggplot(aes(x = movie_count, y = total_revenue)) +
  geom_point(shape = 21, color = "black") + 
  geom_smooth(color = "thistle3", method = "lm", se = FALSE) + 
  theme_minimal()
```

```{r}
yearly.summary2 |>
  ggplot(aes(x = comedy, y = total_revenue)) +
  geom_point(shape = 21, color = "black") + 
  geom_smooth(color = "thistle3", method = "lm", se = FALSE) + 
  theme_minimal()
```



```{r}
mod.full |>
  augment() |>
  ggplot(aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, colour = 'blue') +
  labs(x = 'Fitted Values', y = 'Residuals') +
  ggtitle('Residual vs Fit') +
  theme_bw()
```


```{r}
mod.full |>
  augment() |>
ggplot(aes(sample = .resid)) +
  stat_qq() +
  stat_qq_line() +
  ggtitle('Normal Q-Q Plot') +
  theme_bw()
```

```{r}
shapiro.test(resid(mod.full))
```



### Histogram of movie count 

```{r}
yearly.summary2 |>
  ggplot(aes(x = movie_count)) +
  geom_histogram(bins = 10, fill = "thistle3", color = "black", size = 0.2)+ 
  ggtitle("Histogram of Yearly Movie Count") + 
  theme_minimal() + labs(x = "Yearly Movie Count", y = "Count")

```


### Histogram of comedy count 

```{r}
yearly.summary2 |>
  ggplot(aes(x = comedy)) +
  geom_histogram(bins = 10, fill = "thistle3", color = "black", size = 0.2)+ 
  ggtitle("Histogram of Yearly Comedy Count") + 
  theme_minimal() + labs(x = "Yearly Comedy Count", y = "Count")

```


# Appendix F: What is Disney’s expected total revenue in a year where they release 10 movies and 2 of them are comedies?

```{r}
new = data.frame(comedy = 2, movie_count = 10)
prediction = predict(mod.full,new,interval = "prediction", level = 0.95)
prediction
```



