---
title: "Untitled"
output: html_document
date: "2022-12-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Read In Data Set

```{r}
library(readr)
library(tidyverse)
library(skimr)
disney <- read_csv("/Users/christinalopez/Desktop/STAT471_F22/datasets/disney/disney_movies_total_gross.csv")
```

```{r}
skim_without_charts(disney)
```

# Data Cleaning

```{r}
library(dplyr)

disney2 <- disney |>
  mutate(genre = factor(genre), 
         rating = factor(MPAA_rating, levels = c("G", "PG", "PG-13", "R")), 
         gross = parse_number(inflation_adjusted_gross),
         release_date = as.Date(release_date, format = "%b %d, %Y"),
         release_year = as.numeric(format(release_date, "%Y")),
         gross_million = round(gross/1000000, digits = 1),
         gross_K = round(gross/1000, digits =3)) |>
  select(-total_gross, -inflation_adjusted_gross, -MPAA_rating ) |>
  drop_na() |>
  filter(release_year >= 1992)
```

# Exporatory Data Analysis

## Skim 
```{r}
skim_without_charts(disney2)
```

## Ratings

```{r}

colors = c("thistle3", "thistle4", "rosybrown3", "rosybrown4")

disney2 |>
  group_by(rating) |>
  summarize(n = n()) |>
  ggplot(aes(x = reorder(rating, -n), y = n)) + 
  geom_col(aes(fill = reorder(rating,n)), color = "black", size = 0.2) +   
  scale_fill_manual(values = colors) +
  ggtitle("Top Movie Ratings")+ labs(x = "MPAA Rating", y = "Count") + 
  theme_minimal() + theme(legend.position = "none")


```

## Genres (pink pallet)

```{r}
colors4 = c("thistle4", "thistle3", "rosybrown4", "rosybrown3", "lightpink4", "lightpink3")

disney2 |>
  select(genre) |>
  group_by(genre) |>
  summarise(n = n()) |>
  head(6) |>
  ggplot(aes(x = reorder(genre, -n), y = n)) + 
  geom_col(aes(fill = reorder(genre, -n)), color = "black", size = .2) +
  scale_fill_manual(values = colors4) +
  ggtitle("Top genres") + labs(x = "Genre", y = "Count") + 
  theme_minimal() + theme(legend.position = "none")

```


## Movie Count Per Year 

```{r}
disney2 |>
  select(release_year) |>
  filter(release_year >= 1991) |>
  group_by(release_year) |>
  summarise(n = n()) |>
  ggplot(aes(x = release_year, y = n)) + 
  geom_col(fill = "thistle3", color = "black", size = 0.2)+ 
  ggtitle("Histogram of Movie Release Year") + 
  theme_minimal() + labs(x = "Release Year", y = "Count")
```

# Release Year v Gross

## Linear Plot

```{r}
disney2 |>
  mutate(release_year = as.numeric(release_year)) |>
  ggplot(aes(x = release_year, y = gross_K)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "blue")
```

## Build a model 

```{r}
mod <- disney2 |>
  lm(formula = gross ~ release_year)
summary(mod)

```

```{r}
mod2 <- 
  disney2 |>
  lm(formula = gross ~ genre + rating)

summary(mod2)
```

```{r}
mod3 <- 
  disney2 |>
  lm(formula = gross ~ release_year + genre + rating)

summary(mod3)
```

R^2 are all very low for the models in the movies data set. We don't have the right variables to predict 

So now we want to bring in the yearly revenue data set. 

# Merge in new table for yearly revenue

## Read and join other data set

```{r, message=FALSE, warning=FALSE}
library(readr)
revenue <- read_csv("/Users/christinalopez/Desktop/STAT471_F22/datasets/disney/disney_revenue_1991-2016.csv")

revenue1 <- revenue |>
  mutate(Year = as.numeric(Year))
```

```{r}
disney4 <- disney2 |>
  mutate(Year = release_year)
head(disney4)
```

```{r}
movies.revenue <- disney4 |> inner_join(revenue, by = c("Year" = "Year")) 
head(movies.revenue)
```

# Yearly Summary 

```{r}
yearly.summary <- movies.revenue |>
  group_by(Year, Total) |>
  summarize(movie_count = n()) |>
  rename(total_revenue = Total) |>
  ungroup()
```

## Histogram of revenue

```{r}
yearly.summary |>
  ggplot(aes(x = total_revenue)) +
  geom_histogram(bins = 15, fill = "thistle3", color = "black", size = 0.2)+ 
  ggtitle("Histogram of Yearly Revenue For Disney (Millions of  US $)") + 
  theme_minimal() + labs(x = "Yearly Revenue ($ M)", y = "Count")
```



## Linear graphs 

```{r}
head(yearly.summary)

yearly.summary |>
  ggplot(aes(x = Year, y = total_revenue)) +
  geom_point(shape = 21, color = "black") + 
  geom_smooth(color = "thistle3", method = "lm", se = FALSE) + 
  theme_minimal()
```


```{r}
yearly.summary |>
  ggplot(aes(x = movie_count, y = total_revenue)) +
  geom_point(shape = 21, color = "black") + 
  geom_smooth(color = "thistle3", method = "lm", se = FALSE) + 
  theme_minimal()
```

# Yearly Revenue

## model

```{r}
mod4 <- yearly.summary |>
  lm(formula = total_revenue ~ Year)

summary(mod4)
```

## check line conditions

```{r}
library(broom)

```

```{r}
mod4 |>
  augment() |>
  ggplot(aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, colour = 'blue') +
  labs(x = 'Fitted Values', y = 'Residuals') +
  ggtitle('Residual vs Fit') +
  theme_bw()
```
residual vs fit plot shows that it's a time series data set. We don't have the tools yet to analyze this 

# Movie Count 

## Movie Count Per Year 

```{r}
disney2 |>
  select(release_year) |>
  filter(release_year >= 1991) |>
  group_by(release_year) |>
  summarise(n = n()) |>
  ggplot(aes(x = release_year, y = n)) + 
  geom_col(fill = "thistle3", color = "black", size = 0.2)+ 
  ggtitle("Movie Count Per Year") + 
  theme_minimal() + labs(x = "Release Year", y = "Count")
```

```{r}
mod.moviecount <- yearly.summary |>
  lm(formula = total_revenue ~ movie_count)
```

```{r}
mod.moviecount |>
  augment() |>
  ggplot(aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, colour = 'blue') +
  labs(x = 'Fitted Values', y = 'Residuals') +
  ggtitle('Residual vs Fit') +
  theme_bw()
```


```{r}
mod.moviecount |>
  augment() |>
ggplot(aes(sample = .resid)) +
  stat_qq() +
  stat_qq_line() +
  ggtitle('Normal Q-Q Plot') +
  theme_bw()
```



# Genre Count

```{r}
movies.revenue2 <- movies.revenue |>
  mutate(action = ifelse(genre == "Action", 1, 0),
         adventure = ifelse(genre == "Adventure",1,0),
         musical = ifelse(genre == "Musical", 1, 0),
         drama = ifelse(genre == "Drama", 1, 0),
         comedy = ifelse(genre == "Comedy", 1, 0)) |>
  filter(Year >= 1992)

head(movies.revenue2)
```
## yearly summary with count of top genres

```{r}
yearly.summary2 <- movies.revenue2 |>
  group_by(Year, Total) |>
  summarize(movie_count = n(),
            action_count = sum(action),
            adventure = sum(adventure),
            musical = sum(musical),
            drama = sum(drama),
            comedy = sum(comedy)) |>
  rename(total_revenue = Total) |>
  ungroup()

head(yearly.summary2)
```

## Histogram of movie count 

```{r}
yearly.summary2 |>
  ggplot(aes(x = movie_count)) +
  geom_histogram(bins = 10, fill = "thistle3", color = "black", size = 0.2)+ 
  ggtitle("Histogram of Yearly Movie Count") + 
  theme_minimal() + labs(x = "Yearly Movie Count", y = "Count")

```


## Histogram of comedy count 

```{r}
yearly.summary2 |>
  ggplot(aes(x = comedy)) +
  geom_histogram(bins = 10, fill = "thistle3", color = "black", size = 0.2)+ 
  ggtitle("Histogram of Yearly Comedy Count") + 
  theme_minimal() + labs(x = "Yearly Comedy Count", y = "Count")

```

## model with count of top genres

```{r}
mod5 <- yearly.summary2 |>
  lm(formula = total_revenue ~ comedy + movie_count)
summary(mod5)
```

```{r}
mod5 |>
  augment() |>
  ggplot(aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, colour = 'blue') +
  labs(x = 'Fitted Values', y = 'Residuals') +
  ggtitle('Residual vs Fit') +
  theme_bw()
```

```{r}
mod5 |>
  augment() |>
ggplot(aes(sample = .resid)) +
  stat_qq() +
  stat_qq_line() +
  ggtitle('Normal Q-Q Plot') +
  theme_bw()
```
```{r}
shapiro.test(resid(mod5))

```



```{r}
yearly.summary2 |>
  ggplot(aes(x = musical + comedy, y = total_revenue)) +
  geom_point(shape = 21, color = "black") + 
  geom_smooth(color = "thistle3", method = "lm", se = FALSE) + 
  theme_minimal()
```

```{r}
yearly.summary2 |>
  mutate(music.comedy = musical + comedy)
```



# Challenges 

- Translate gross revenue from a text variable to a numeric variable 
- We can't get a very high R^2 value with the variables we have in this data set






